%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Benjamin L Hili} \\ \vspace{1pt}
    \small +1 920 659 6449 $|$ \href{mailto:ben.hili1994@gmail.com}{\underline{ben.hili1994@gmail.com}} $|$ 
    \href{https://github.com/benhili}{\underline{github.com/benhili}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western Sydney University}{Parramatta, NSW}
      {Bachelor of Computer Science, Major in Systems Programming}{2014 -- 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{September 2020 -- Present}
      {Vodafone}{North Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Worked within the identity and access management team to develop a new login and registration flow for new and existing customers using Auth0.}
        \resumeItem{Created microservices on AWS Lambda for custom business requirements for multifactor authentication and custom multi-step registration flows.}
        \resumeItem{Fleshed out the integration and unit testing pipelines using Jest, Cypress and puppeteer.}
        \resumeItem{Extended CI/CD pipeline to automatically test and deploy changes via AWS cloudformation.}
        \resumeItem{Built responsive and stylised user flows on the front end with React and Styled components.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer}{August. 2019 -- September 2020}
      {Linktree}{Collingwood, VIC}
      \resumeItemListStart
        \resumeItem{Created a security service using the node runtime in AWS Lambda to capture user data, flag actions that violated our ToS and process offending accounts via SQS. The accounts would then be disabled and informed them of the reason they were banned on their next login.}
        \resumeItem{Migrated a large portion of our PHP/Symfony codebase into NextJS allowing for faster development for our React team and providing much faster page loads at a lower server cost.}
        \resumeItem{Created Lambdas triggered via SNS events which would clean and persist event logs from our frontend. This provided us with a wealth of data regarding user actions on our platform and could be used by our data scientists to provide insights in new features and their relative value to our users.}
        \resumeItem{Migrated AWS EKS cluster to Kubernetes saving resources and giving us finer control. Migrated our primary application from Vagrant to Docker which reduced the complexity and time taken to get the latest build running locally.}
        \resumeItem{Wrote automated tests for all of our untested Node services using Jest and added them to our CircleCi and Buildkite pipelines.}
        \resumeItem{Wrote GraphQL APIs for our microservices using type-graphql so that our frontend could more easily retrieve required user data.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{December 2018 -- July 2019}
      {Spitfire Corporation}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Worked with a small team to develop a Portfolio Management System allowing easy access, analysis and management of client portfolios as well as automated insights to guide investment decisions. Created using Flask and hosted on Amazon EC2 instances.}
        \resumeItem{Created an application to automate internal workflows using Django and GraphQL removing the need for hours of repeated manual effort per week spent on data entry.}
        \resumeItem{Created Django backend accessible via GraphQL API and consumed using Vue and Apollo Client to provide a web client to allow internal staff to kick off serverless workflows and to view and modify their results.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Security Developer}{July 2018 -- December 2018}
      {Westpac}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Developed a web application to automate business logic for manual tasks which saved days of manual effort each month. Created using Python/Flask and hosted on our internal network.}
        \resumeItem{Developed a big data pipeline to process and visualize data from a variety of systems saving approximately a week of manual searching and processing for reports each month, written using Apache Spark within Palantir Foundry.}
        \resumeItem{Made small updates and maintenance changes to a large Springboot application that was used internally for recording the outcomes of cyber security penetration tests.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{April 2017 -- February 2018}
      {Inspired Software}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Designed and implemented front ends for e-commerce web applications for our clients using Django, Sass and Javascript.}
        \resumeItem{Bash scripting and automation, creating docker containers for our codebases, building devops pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{June 2016 -- April 2017}
      {Cubesys Pty. Ltd}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Using .Net, JQuery and Ajax, created a guest WiFi web application for a government client in the healthcare sector.}
        \resumeItem{Created an admin application giving internal users standard operations across our Azure virtual machines using .Net.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:}{ Javascript/Typescript, Python, SQL, PHP, Elixir, CSS/SASS } \\
     \textbf{Frameworks:}{ NextJS, Flask, Django, React, Vue, Symfony, NestJS, Phoenix, Bulma, Gatsby } \\
     \textbf{Tools:}{ Kubernetes, Docker, Pandas, AWS, Postgres, Redis, Terraform, Ansible } \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}