%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Benjamin L Hili} \\ \vspace{1pt}
  \small 0414 501 009 $|$ \href{mailto:ben.hili1994@gmail.com}{\underline{ben.hili1994@gmail.com}} $|$
  \href{https://github.com/benhili}{\underline{github.com/benhili}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Western Sydney University}{Parramatta, NSW}
{Bachelor of Computer Science, Major in Systems Programming}{2014 -- 2018}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Senior Software Engineer}{May 2023 -- Present}
{IAG}{Sydney, Vic}
\resumeItemListStart
\resumeItem{Wrote abstractions to allow new features to be re-used across all of IAG's brands and partner brands}
\resumeItem{Built a dashboard to allow returning customers to identify themselves and add other existing customers to an insurance policy}
\resumeItem{Added new services in the NestJS backend to provide email updates and allow users to save their sessions in DynamoDB}
\resumeItemListEnd

\resumeSubheading
{Senior Software Engineer}{Mar 2022 -- Apr 2023}
{Qantas}{Melbourne, Vic}
\resumeItemListStart
\resumeItem{Extended Clojure APIs to support payment using a combination of points and cash}
\resumeItem{Rewrote old logic around mapping flight pairs and hotels when booking holiday packages, taking local timezones into consideration }
\resumeItem{Assisted in creating a wiki to collate the API documentation for our microservices}
\resumeItemListEnd

\resumeSubheading
{Senior Software Engineer}{August 2021 -- Feb 2022}
{Latitude Financial}{Melbourne, Vic}
\resumeItemListStart
\resumeItem{Worked with KYC (know your customer) team to develop Golang microservices to determine loan repayability for customers that are applying for Latitudes buy-now-pay-later (BNPL) product}
\resumeItem{Built abstractions to allow Latitude's existing backend services to be used in the NZ market with only minor changes required to support region-specific rules}
\resumeItem{Extended logging and metrics to enable tracing of a customers end-to-end journey through our various services to enable easier debugging of production issues as well as better monitoring and alerting}
\resumeItem{Mentoring junior developers via pair programming sessions and ran a dev guild, including monthly workshops for AWS, Golang and patterns like TDD}
\resumeItemListEnd

\resumeSubheading
{Senior Software Engineer}{September 2020 -- August 2021}
{Vodafone}{North Sydney, NSW}
\resumeItemListStart
\resumeItem{Worked in a small team to replace Vodafone's existing IAM system with Auth0 and create a new login flow in React.}
\resumeItem{Wrote scripts and created new lambdas to maintain backward compatibility with the legacy IAM system, preventing the need for re-registration by existing users.}

\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Software Engineer}{August. 2019 -- September 2020}
{Linktree}{Collingwood, VIC}
\resumeItemListStart
\resumeItem{Created an event-driven system using AWS Lambda and to capture user data, flag actions that violated our ToS and process offending accounts via SQS.}
\resumeItem{Migrated a large portion of our PHP/Symfony codebase into NextJS allowing for faster development for our React team and providing much faster page loads at a lower server cost.}
\resumeItem{Created Lambdas triggered via SNS events which would clean and persist event logs from our frontend. This provided us with a wealth of data regarding user actions on our platform and was used by our data team to provide insights into new features and their value to our users.}
\resumeItem{Migrated AWS EKS cluster to Kubernetes saving resources and giving us finer control. Migrated our primary application from Vagrant to Docker which reduced the complexity and time taken to build the application.}
\resumeItem{Wrote automated tests for all of our untested Node services using Jest and added them to our CircleCi and Buildkite pipelines.}
\resumeItem{Wrote GraphQL APIs for our microservices using type-graphql so that our frontend could more easily retrieve required user data.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{December 2018 -- July 2019}
{Spitfire Corporation}{Sydney, NSW}
\resumeItemListStart
\resumeItem{Developed a robo-trader POC with Python to generate potential sequences of trades to rebalance client's portfolios.}
\resumeItem{Created a CMS using Django for traders to access and visualise the API-generated information.}
\resumeItem{Deployed infrastructure to AWS using Terraform and established a CI/CD pipeline.}
\resumeItemListEnd

\resumeSubheading
{Security Developer}{July 2018 -- December 2018}
{Westpac}{Sydney, NSW}
\resumeItemListStart
\resumeItem{Automated report generation from pen-testing data using Palantir Foundry to highlight high-severity issues for faster remediation.}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{April 2017 -- February 2018}
{Inspired Software}{Sydney, NSW}
\resumeItemListStart
\resumeItem{Developed software solutions for multiple small businesses, including warehouse inventory management, e-commerce and accounting using Odoo.}
\resumeItemListEnd

\resumeSubheading
{Web Developer}{June 2016 -- April 2017}
{Cubesys Pty. Ltd}{Sydney, NSW}
\resumeItemListStart
\resumeItem{Developed software solutions for NSW Health, including the WiFi portal for Westmead Children's Hospital as the sole developer.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages:}{ Javascript/Typescript, Python, SQL, PHP, Elixir, CSS/SASS } \\
        \textbf{Frameworks:}{ NextJS, Flask, Django, React, Vue, Symfony, NestJS, Phoenix, Bulma, Gatsby } \\
        \textbf{Tools:}{ Kubernetes, Docker, Pandas, AWS, Postgres, Redis, Terraform, Ansible } \\
        }}
\end{itemize}


%-------------------------------------------
\end{document}
